\documentclass{csexam}

\usepackage{listings}
\usepackage{xcolor}

% Python code styling
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue}\bfseries,
    stringstyle=\color{red},
    commentstyle=\color{green!50!black}\itshape,
    showstringspaces=false,
    breaklines=true,
    frame=single,
    numbers=left,
    numberstyle=\tiny\color{gray}
}

% Course information
\course{CSCI 128: Introduction to Computer Science}
\courseshort{CSCI 128}
\exam{Quiz 8: Advanced Sound Techniques}
\examdate{Winter 2025}

\begin{document}

\maketitle

\begin{rules}
\textbf{Instructions:}
\begin{itemize}
    \item This quiz should take approximately 15 minutes.
    \item Answer all questions in the space provided.
    \item Show your work where applicable.
    \item No calculators or electronic devices allowed.
\end{itemize}
\end{rules}

\showgrade

\begin{questions}

\question[5] Explain how an echo effect is created in digital audio. What two key parameters are needed?

\vspace{1.8in}

\question[5] Complete the code to create a simple echo effect by overlaying a delayed, quieter version:

\begin{lstlisting}
from pydub import AudioSegment

def add_echo(sound, delay_ms, volume_decrease):
    # Create silence for delay
    silence = AudioSegment.silent(duration=______)

    # Make echo quieter
    echo = sound - ___________

    # Add delay before echo
    delayed_echo = _______ + echo

    # Overlay on original
    return sound.overlay(____________)
\end{lstlisting}

\question[4] What is the difference between overlaying two sounds and concatenating them?

\vspace{1.5in}

\question[3] If you mix two sound clips of equal volume together, why might the result be distorted or clipped?

\vspace{1.3in}

\question[4] Write code to splice together three sound files (intro.mp3, middle.mp3, outro.mp3) in sequence:

\vspace{2in}

\question[4] Short answer:

\begin{parts}
\part What does normalization do to a sound file?

\vspace{0.8in}

\part Why would you fade in or fade out audio?

\vspace{0.8in}

\part What is the purpose of splitting stereo sound into left and right channels?

\vspace{0.8in}
\end{parts}

\end{questions}

\end{document}
