\documentclass{csexam}

\usepackage{listings}
\usepackage{xcolor}

% Python code styling
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue}\bfseries,
    stringstyle=\color{red},
    commentstyle=\color{green!50!black}\itshape,
    showstringspaces=false,
    breaklines=true,
    frame=single,
    numbers=left,
    numberstyle=\tiny\color{gray}
}

% Course information
\course{CSCI 128: Introduction to Computer Science}
\courseshort{CSCI 128}
\exam{Quiz 4}
\examdate{Winter 2025}

\begin{document}

\maketitle

\begin{rules}
\textbf{Instructions:}
\begin{itemize}
    \item This quiz covers material from Lectures 7-8 (Functions and Advanced Functions)
    \item Answer all questions in the space provided
    \item Show your work where applicable
    \item Time limit: 15 minutes
\end{itemize}
\end{rules}

\vspace{0.2in}

\showgrade

\newpage

\begin{questions}

\question[1] What is the purpose of defining a function in Python? Give one benefit of using functions.
\vspace{1.5in}

\question[1] What is the difference between a function parameter and a function argument?
\vspace{1.5in}

\question[1] What will the following code print?
\begin{lstlisting}[numbers=none]
def double(x):
    return x * 2

result = double(5)
print(result)
\end{lstlisting}
Answer: \underline{\hspace{1in}}

\question[3] Write a Python function called \texttt{area\_of\_circle} that takes a radius as a parameter and returns the area of the circle. Use $\pi \approx 3.14159$.
\vspace{1.5in}

\question[2] What is the difference between a function that uses \texttt{return} and a function that uses \texttt{print}?
\vspace{1.5in}

\question[2] What is a default parameter value? Give an example of when you might use one.
\vspace{1.5in}

\question[3] Consider the following function:
\begin{lstlisting}[numbers=none]
def greet(name, greeting="Hello"):
    return f"{greeting}, {name}!"
\end{lstlisting}
What will be the output of:
\begin{parts}
    \part \texttt{greet("Alice")} \hfill \underline{\hspace{2in}}
    \part \texttt{greet("Bob", "Hi")} \hfill \underline{\hspace{2in}}
\end{parts}

\question[2] What is variable scope? Why does it matter in functions?
\vspace{1.5in}

\end{questions}

\end{document}
