\documentclass{csexam}

\usepackage{listings}
\usepackage{xcolor}

% Python code styling
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue}\bfseries,
    stringstyle=\color{red},
    commentstyle=\color{green!50!black}\itshape,
    showstringspaces=false,
    breaklines=true,
    frame=single,
    numbers=left,
    numberstyle=\tiny\color{gray}
}

% Course information
\course{CSCI 128: Introduction to Computer Science}
\courseshort{CSCI 128}
\exam{Quiz 5}
\examdate{Winter 2025}

\begin{document}

\maketitle

\begin{rules}
\textbf{Instructions:}
\begin{itemize}
    \item This quiz covers material from Lectures 7-8 (Sound Basics and Advanced Sound)
    \item Answer all questions in the space provided
    \item Show your work where applicable
    \item Time limit: 15 minutes
\end{itemize}
\end{rules}

\vspace{0.2in}

\showgrade

\newpage

\begin{questions}

\question[2] Compare digital images and digital sounds by completing the table:
\begin{center}
\begin{tabular}{l|l|l}
    & \textbf{Images} & \textbf{Sounds} \\
    \hline
    Basic unit & Pixel & \underline{\hspace{1in}} \\
    Dimensions & 2D (width × height) & \underline{\hspace{1in}} \\
\end{tabular}
\end{center}

\question[2] What is a sample in digital audio? What does the sample value represent?
\vspace{1.5in}

\question[2] What is sample rate? If a sound has a sample rate of 44,100 Hz, what does this mean?
\vspace{1.5in}

\question[2] What happens to a sound when you increase all sample values by a constant amount versus multiplying all sample values by a constant?
\vspace{1.5in}

\question[3] Write Python code to reverse a sound. Assume you have a list called \texttt{samples} containing all the sound samples.
\vspace{1.5in}

\question[2] Explain the difference between changing the volume of a sound and changing its pitch.
\vspace{1.5in}

\question[2] What is sound mixing? If you want to mix two sounds together, what operation do you perform on their corresponding samples?
\vspace{1.5in}

\end{questions}

\end{document}
