\documentclass{csexam}

\usepackage{listings}
\usepackage{xcolor}

% Python code styling
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue}\bfseries,
    stringstyle=\color{red},
    commentstyle=\color{green!50!black}\itshape,
    showstringspaces=false,
    breaklines=true,
    frame=single,
    numbers=left,
    numberstyle=\tiny\color{gray}
}

% Course information
\course{CSCI 128: Introduction to Computer Science}
\courseshort{CSCI 128}
\exam{Quiz 11: Web Data and Information}
\examdate{Winter 2025}

\begin{document}

\maketitle

\begin{rules}
\textbf{Instructions:}
\begin{itemize}
    \item This quiz should take approximately 15 minutes.
    \item Answer all questions in the space provided.
    \item Show your work where applicable.
    \item No calculators or electronic devices allowed.
\end{itemize}
\end{rules}

\showgrade

\begin{questions}

\question[5] What does CSV stand for? Describe the format and give an example of 2 rows with 3 columns.

\vspace{1.8in}

\question[5] Complete the code to read a CSV file with headers and print each row:

\begin{lstlisting}
import _____

with open("data.csv", "r") as file:
    reader = csv.________(file)
    for row in reader:
        name = row['_____']
        age = row['_____']
        print(f"{name} is {age} years old")
\end{lstlisting}

\question[4] What is the difference between \texttt{csv.reader()} and \texttt{csv.DictReader()}?

\vspace{1.5in}

\question[4] Write code to create a CSV file with headers "filename", "width", "height":

\vspace{2.3in}

\question[5] Given this JSON data:

\begin{lstlisting}[numbers=none]
{
  "images": [
    {"file": "photo1.jpg", "tags": ["beach", "sunset"]},
    {"file": "photo2.jpg", "tags": ["mountain"]}
  ]
}
\end{lstlisting}

Write code to load this file and print all filenames:

\vspace{2in}

\question[4] Short answer questions about data formats:

\begin{parts}
\part What advantage does JSON have over CSV for complex data?

\vspace{0.9in}

\part When would you choose CSV over JSON?

\vspace{0.9in}

\part What does it mean for JSON data to be "hierarchical"?

\vspace{0.9in}
\end{parts}

\question[3] Why might you create a CSV report of all images in a directory? Give two practical use cases.

\vspace{1.5in}

\end{questions}

\end{document}
