\documentclass{csexam}

\usepackage{listings}
\usepackage{xcolor}

% Python code styling
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue}\bfseries,
    stringstyle=\color{red},
    commentstyle=\color{green!50!black}\itshape,
    showstringspaces=false,
    breaklines=true,
    frame=single,
    numbers=left,
    numberstyle=\tiny\color{gray}
}

% Course information
\course{CSCI 128: Introduction to Computer Science}
\courseshort{CSCI 128}
\exam{Quiz 6}
\examdate{Winter 2025}

\begin{document}

\maketitle

\begin{rules}
\textbf{Instructions:}
\begin{itemize}
    \item This quiz covers material from Lecture 9 (Building Bigger Programs)
    \item Answer all questions in the space provided
    \item Show your work where applicable
    \item Time limit: 15 minutes
\end{itemize}
\end{rules}

\vspace{0.2in}

\showgrade

\newpage

\begin{questions}

\question[2] What are three benefits of organizing your code into functions?
\vspace{1.5in}

\question[2] What is a module in Python? How do you import a function from a custom module?
\vspace{1.5in}

\question[3] What is the purpose of the following line at the end of a Python file?
\begin{lstlisting}[numbers=none]
if __name__ == "__main__":
    main()
\end{lstlisting}
\vspace{1.5in}

\question[2] What is the difference between testing code interactively and writing test functions?
\vspace{1.5in}

\question[3] Write a function called \texttt{increase\_brightness} that takes an image as a parameter and returns a new image with all RGB values increased by 20 (without exceeding 255).
\vspace{1.5in}

\question[3] What is debugging? Name two strategies for debugging a program that isn't working correctly.
\vspace{1.5in}

\end{questions}

\end{document}
