\documentclass{csexam}

\usepackage{listings}
\usepackage{xcolor}

% Python code styling
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue}\bfseries,
    stringstyle=\color{red},
    commentstyle=\color{green!50!black}\itshape,
    showstringspaces=false,
    breaklines=true,
    frame=single,
    numbers=left,
    numberstyle=\tiny\color{gray}
}

% Course information
\course{CSCI 128: Introduction to Computer Science}
\courseshort{CSCI 128}
\exam{Quiz 9: Building Bigger Programs}
\examdate{Winter 2025}

\begin{document}

\maketitle

\begin{rules}
\textbf{Instructions:}
\begin{itemize}
    \item This quiz should take approximately 15 minutes.
    \item Answer all questions in the space provided.
    \item Show your work where applicable.
    \item No calculators or electronic devices allowed.
\end{itemize}
\end{rules}

\showgrade

\begin{questions}

\question[5] What are the benefits of organizing code into functions? List at least three.

\vspace{1.5in}

\question[4] Complete the function that applies a filter to an image based on a string parameter:

\begin{lstlisting}
def apply_filter(img, filter_name):
    """Apply the specified filter to the image."""
    if filter_name == "grayscale":
        return _________________
    elif filter_name == "negative":
        return _________________
    elif filter_name == "sepia":
        return _________________
    else:
        return img  # No filter
\end{lstlisting}

\question[5] Explain the difference between a function parameter and a function return value. Provide an example.

\vspace{2in}

\question[3] What is a module in Python? How do you import a function from a custom module?

\vspace{1.5in}

\question[4] Identify what's wrong with this function and fix it:

\begin{lstlisting}
def double_number(x):
    x = x * 2

result = double_number(5)
print(result)  # Expected: 10, but prints None
\end{lstlisting}

\vspace{1.5in}

\question[4] Short answer questions about program organization:

\begin{parts}
\part What is the purpose of docstrings in Python functions?

\vspace{0.8in}

\part Why should functions have descriptive names?

\vspace{0.8in}

\part What does it mean for a function to have a "single responsibility"?

\vspace{0.8in}
\end{parts}

\end{questions}

\end{document}
