\documentclass{csexam}

\usepackage{listings}
\usepackage{xcolor}

% Python code styling
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue}\bfseries,
    stringstyle=\color{red},
    commentstyle=\color{green!50!black}\itshape,
    showstringspaces=false,
    breaklines=true,
    frame=single,
    numbers=left,
    numberstyle=\tiny\color{gray}
}

% Course information
\course{CSCI 128: Introduction to Computer Science}
\courseshort{CSCI 128}
\exam{Quiz 6: Collages and Combining Images}
\examdate{Winter 2025}

\begin{document}

\maketitle

\begin{rules}
\textbf{Instructions:}
\begin{itemize}
    \item This quiz should take approximately 15 minutes.
    \item Answer all questions in the space provided.
    \item Show your work where applicable.
    \item No calculators or electronic devices allowed.
\end{itemize}
\end{rules}

\showgrade

\begin{questions}

\question[5] Complete the code to paste one image onto another at position (100, 50):

\begin{lstlisting}
from PIL import Image

canvas = Image.new("RGB", (800, 600), (255, 255, 255))
photo = Image.open("photo.jpg")

# Paste photo onto canvas at (100, 50)
canvas._______(photo, (_____, _____))

canvas.save("collage.jpg")
\end{lstlisting}

\question[4] Explain the difference between copying pixels manually versus using Pillow's \texttt{paste()} method:

\vspace{1.5in}

\question[5] Write code to copy a rectangular region from one image to another. Copy pixels from (50, 50) to (150, 150) in \texttt{source\_img} and paste them at (200, 100) in \texttt{dest\_img}:

\vspace{2.5in}

\question[3] You want to create a 2×2 grid collage from 4 images, each 400×300 pixels. What should be the dimensions of your canvas?

Width: \underline{\hspace{1in}} pixels

Height: \underline{\hspace{1in}} pixels

\vspace{0.5in}

\question[3] What will happen if you try to paste an image at position (700, 500) on a canvas that is 800×600 pixels, and the image being pasted is 200×200 pixels?

\vspace{1.2in}

\question[5] Short answer questions about image compositing:

\begin{parts}
\part What is a canvas in the context of creating collages?

\vspace{0.7in}

\part Why might you create a white or black canvas before pasting images?

\vspace{0.7in}

\part What is the purpose of calculating positions when creating a grid collage?

\vspace{0.7in}
\end{parts}

\end{questions}

\end{document}
