\documentclass{csexam}

\usepackage{listings}
\usepackage{xcolor}

% Python code styling
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue}\bfseries,
    stringstyle=\color{red},
    commentstyle=\color{green!50!black}\itshape,
    showstringspaces=false,
    breaklines=true,
    frame=single,
    numbers=left,
    numberstyle=\tiny\color{gray}
}

% Course information
\course{CSCI 128: Introduction to Computer Science}
\courseshort{CSCI 128}
\exam{Quiz 7: Sound Processing Basics}
\examdate{Winter 2025}

\begin{document}

\maketitle

\begin{rules}
\textbf{Instructions:}
\begin{itemize}
    \item This quiz should take approximately 15 minutes.
    \item Answer all questions in the space provided.
    \item Show your work where applicable.
    \item No calculators or electronic devices allowed.
\end{itemize}
\end{rules}

\showgrade

\begin{questions}

\question[5] Short answer questions about digital sound:

\begin{parts}
\part What is a sound sample?

\vspace{0.8in}

\part What is sampling rate and what unit is it measured in?

\vspace{0.8in}

\part What does amplitude represent in a sound wave?

\vspace{0.8in}

\part What is the standard sampling rate for CD-quality audio?

\vspace{0.5in}
\end{parts}

\question[4] Fill in the blanks to complete the code that loads a sound file:

\begin{lstlisting}
from pydub import _________

sound = AudioSegment.from_______("music.mp3")

# Get properties
duration = len(sound)  # in ___________
sample_rate = sound.frame_______
\end{lstlisting}

\question[5] Write code to increase the volume of a sound by 10 dB and save it:

\vspace{2.5in}

\question[3] If a sound file is 5 seconds long with a sampling rate of 44,100 Hz, how many samples does it contain?

Show your work:

\vspace{1.5in}

\question[3] What is the difference between increasing volume by changing amplitude versus using dB scaling?

\vspace{1.5in}

\question[5] Match each operation with its effect on sound:

\begin{parts}
\part Reversing samples \hspace{1in} \underline{\hspace{1.5in}}

\part Halving all sample values \hspace{0.5in} \underline{\hspace{1.5in}}

\part Doubling sampling rate \hspace{0.7in} \underline{\hspace{1.5in}}

\part Setting all samples to 0 \hspace{0.7in} \underline{\hspace{1.5in}}

\vspace{0.3in}

Options: A) Silence B) Plays backwards C) Quieter D) Higher pitch
\end{parts}

\end{questions}

\end{document}
